---
title: "Travel Time"
author: "PSU"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(dygraphs)

# read-in data for dygraphs
nb_i5_jantzen_tt_xts <- readRDS("data/nb_i5_jantzen_tt_xts.rds")
nb_i205_airport_tt_xts <- readRDS("data/nb_i205_airport_tt_xts.rds")
sb_i205_padden_tt_xts <- readRDS("data/sb_i205_padden_tt_xts.rds")
```

## Methods
Date range of comparison is 2019-02-03 through 2019-03-03.
Highway corridors selected are:
- I-5 NB, Jantzen Beach to Main St.
- I-205 NB, Airport Way to Padden Parkway
- I-205 SB, Padden Parkway to Airport Way
- SR 14 EB, MP 1.93 to Ellsworth
- SR 14 WB, Ellsworth to MP 1.93

TMC segments were approximately selected in relation to selected WSDOT stations (see map).

### Data collection
_INRIX_
Raw one minute data were used to calculate travel time along each highway segment and then averaged hourly. Data with a confidence score less than 30, C-Value less than 75, and NAs were excluded. If a TMC segment had missing data then the hourly averaged travel time for that corridor was excluded for that hour.

_WSDOT/PORTAL_
WSDOT travel time calculations are calculated by PORTAL using raw five minute data, averaged hourly for each station, and then summed for the selected stations along a corridor. If there are missing averaged hourly data at any station along a selected corridor, travel time for that corridor were excluded for that hour.

## Results
### I-5 NB, Janzten Beach to Main St.
```{r nb_i5_janzten, echo = F}
dygraph(nb_i5_jantzen_tt_xts)
```

### I-205 NB, Airport Way to Padden Parkway
```{r nb_i205_airport, echo = F}
dygraph(nb_i205_airport_tt_xts)
```

### I-205 SB, Padden Parkway to Airport Way
```{r sb_i205_padden, echo = F}
dygraph(sb_i205_padden_tt_xts)
```

