---
title: "Travel Time"
author: "PSU"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(dygraphs)

# read-in data for dygraphs
nb_i5_jantzen_tt_xts <- readRDS("data/nb_i5_jantzen_tt_xts.rds")
nb_i205_airport_tt_xts <- readRDS("data/nb_i205_airport_tt_xts.rds")
sb_i205_padden_tt_xts <- readRDS("data/sb_i205_padden_tt_xts.rds")
```

## Methods
Date range of comparison is 2019-02-03 through 2019-03-03.
Corridors selected are:
- I-5 NB, Jantzen Beach to Main St.
- I-205 NB, Airport Way to Padden Parkway
- I-205 SB, Padden Parkway to Airport Way

### Data collection
_INRIX_
Raw, one minute data were used. For hourly averaged travel time along the corridor, data with a confidence score less than 30 (3% of available data), C-Value less than 75, and NA were excluded.


## Results
### I-5 NB, Janzten Beach to Main St.
```{r nb_i5_janzten, echo = F}
dygraph(nb_i5_jantzen_tt_xts)
```

### I-205 NB, Airport Way to Padden Parkway
```{r nb_i205_airport, echo = F}
dygraph(nb_i205_airport_tt_xts)
```

### I-205 SB, Padden Parkway to Airport Way
```{r sb_i205_padden, echo = F}
dygraph(sb_i205_padden_tt_xts)
```

